Flatiron cleaning

### 2021-10-21 Rmd/rdi analysis.Rmd
Update report

  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # Calculate CrCl
  inner_join(., clinical_data %>% select(-surgerydate),
             by = "patientid") %>% 
  mutate(CrCl = (
       (
    ((140 - ageatdx) * weight) /
    (72 * creatinine)
       ) *
    0.85)
  ) %>% 
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>%

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

@@

  mutate(relative_dose_intensity = amount / expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug < 1                ~ "correct",
    mean_RDI_per_drug == 1                 ~ "perfect",
    mean_RDI_per_drug > 1 &
      mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("perfect", "correct", "higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>
<br>

@@

## Univariable
```{r Table 5 HR}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- tbl5 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- tbl6 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Pacli
tbl7 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
tbl7 <- tbl7 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl8 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl8 <- tbl8 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl9 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl9 <- tbl9 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# PPB
tbl10 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl12 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl12 <- tbl12 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- tbl13 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl13$month_at_os, event = tbl13$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- tbl14 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl14$month_at_os, event = tbl14$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- tbl15 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl15$month_at_os, event = tbl15$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()

@@

## Multivariable
`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os, 
             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()

tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os, 
             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os, 
             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- 
  coxph(Surv(time = tbl4$month_at_os, 
             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- 
  coxph(Surv(time = tbl5$month_at_os, 
             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- 
  coxph(Surv(time = tbl6$month_at_os, 
             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

>>>>

  # Calculate ideal dody weight
  mutate(ideal_weight = case_when(
    height <= 1.524               ~ 45.5 + 2.3,
    height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
  )) %>% 
  mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
  ) %>% 
  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%

  mutate(actual_bmi = weight / (height * height)) %>%
  mutate(actual_bmi_cat = case_when(
    actual_bmi < 25                    ~ "Underweight and normal weight",
    actual_bmi >= 25 &
      actual_bmi < 30                  ~ "Overweight",
    actual_bmi >= 30                   ~ "Obese"
  )) %>%
  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
  # Calculate CrCl
  inner_join(., clinical_data %>% select(-surgerydate),
             by = "patientid") %>% 
  mutate(CrCl = (
       (
    ((140 - ageatdx) * weight) /
    (72 * creatinine)
       ) *
    0.85)
  ) %>% 
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    actual_bmi >= 25                  ~ CrCl,
    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
  )) %>% 
  mutate(adjusted_CrCl = case_when(
    adjusted_CrCl > 125               ~ 125,
    TRUE                              ~ adjusted_CrCl
  )) %>%

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

@@

  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "correct",
    mean_RDI_per_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_drug >= 0.75 &
      mean_RDI_per_drug < 0.85             ~ "underdose",
    mean_RDI_per_drug >= 0.85 &
      mean_RDI_per_drug <= 1                ~ "correct",
    # mean_RDI_per_drug == 1                 ~ "perfect",
    # mean_RDI_per_drug > 1 &
    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
    mean_RDI_per_drug > 1               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("correct", #"perfect", #"higher dose", 
                                     "overdose", 
                                     "highly underdose", "underdose")))
```
<br>
<br>
<br>

@@

## Univariable
```{r Table 5 HR}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- tbl5 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- tbl6 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Pacli
tbl7 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
tbl7 <- tbl7 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl8 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl8 <- tbl8 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl9 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl9 <- tbl9 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# PPB
tbl10 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl12 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl12 <- tbl12 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- tbl13 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- tbl14 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- tbl15 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

@@

## Multivariable
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- 
  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- 
  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- 
  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()
